MRD_final_microbiome

### 2019-12-03 import_popln_age_data.Rmd
updated

final <- plot_grid(p1, p2,p3,p4,p5,p6, labels = c('A', 'B','C', 'D','E', 'F'),ncol = 2)
ggsave("overview.jpg", final) 
```

>>>>

p7 <- ggplot(ad.p.melt, aes(x = variable, y = value, colour = Location)) + 
  geom_line() + 
  ylab(label="AD Prevalance") + 
  xlab("Year") 
legend <- get_legend(p7)

final <- plot_grid(p1, p2,p3,p4,p5,p6, labels = c('A', 'B','C', 'D','E', 'F'),ncol = 2)
ggsave("overview.jpg", final,width = 20, height = 20, units = "cm") 
```
